Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
some changes to the synthesis sec

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach,
we compute the set of reachable states by finding 
a completeness threshold $\overline{k}$.
Essentially, $\overline{k}$ represents the number of iterations 
to sufficiently unwind the closed-loop state-space system 
so that the variation rate (derivative) of the states is negligible, 
ensuring that the boundaries are not violated for any $k>\overline{k}$. 
Then, it is sufficient to unwound the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds.

>>>>

The controller synthesis is described in Fig.~\ref{fig:CEGIS-precision-increment}.
One important observation is that, for this approach,
we compute the set of reachable states by finding 
a completeness threshold $\overline{k}$.
Essentially, $\overline{k}$ represents the number of iterations 
required to sufficiently unwind the closed-loop state-space system 
such that the boundaries are not violated for any $k>\overline{k}$
(i.e. it's sufficient to unwound the closed-loop state-space system up to  
$\overline{k}$ in order to ensure that $\phi_{safety}$ holds).
